---
title: "Homework 10"
author: "Michael Yan"
date: "June 21, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r, message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
library(knitr)
library(rgl)
data <- read_csv("Hw10Data.csv") 
Table <- table(data$Pain, data$Treatment) %>% kable()
Table
invisible(as.factor(data$Pain))

#Make Pain numeric - Yes="1", and No="0". 
pain1 <- ifelse (data$Pain == "No", 0, 1)
#Fit a logistic model for response variable pain predicted by age, treatment and their interaction. 
modelfit <- glm(pain1 ~ Age*Treatment, data=data, family = "binomial")
#A summary of the model, giving us values and model. 
summary(modelfit)

#predict probability of pain for treatment A and B as well as Age of 70. 
predict(modelfit, newdata = data.frame(Age=c(70,70), Treatment=c("A", "B")), type="response")

#estimate odds for someone aged 70 and a treatment of A
exp(predict(modelfit, newdata=data.frame(Age=70, Treatment="A", type="Link")))
#Plotting the variables in a logistic model. 
plots <- ggiraphExtra::ggPredict(modelfit)
plots
```
From our model and our plots, we can conclude that there is a linear relationship for the placebo vs a logistic relationship for the drugs A and B. The placebo effect is represented by the blue line and denoted as "P". We can also interpret the idea that patients given the placebo does not show a significant effect on the pain, whereas patients given the treatments A and B have a lower rate of experiencing pain. This goes to say that the treatment effect has a large impact on the response variable. (Similar to the idea of a hypothesis test!)