---
title: "Homework 9"
author: "Michael Yan"
date: "June 17, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Reading in Data
```{r, message=FALSE}
library(tidyverse)
library(dplyr)
data <- read.csv("forestFiresTrain.csv") %>% filter(area!=0) %>% mutate(Logarea=log(area)) 
subdata <- data %>% select(month, day, Logarea, temp, RH, wind, area)
```

#Process

Overall, to help predict the log of the area, I had decided to consider several variables. For one, I had chosen the RH and the temp Variables as to help predict my log variable. Looking at our fitted models and their respective adjusted R-Squares and AICc, AIC, and BICs, we see that the area variable is the best variable in explaining the log of the area. However, I had chosen to go with Relative humidity and temperature because there is some inherent bias and that the area variable is simply not a good variable to choose from. 

Our next model would go to RH and temperature since it has a slightly higher adjusted R-square and has lower statistics values representing the AICc, BIC, and the AIC. 

```{r model, warning=FALSE, message=FALSE}

library(rgl)
library(stats)
library(ggplot2)

mlrfit1 <- lm(Logarea ~ area, data=subdata)
mlrfit2 <- lm(Logarea ~ temp, data=subdata)
mlrfit3 <- lm(Logarea ~ RH+wind, data=subdata)
mlrfit4 <- lm(Logarea ~ month+temp, data=subdata)
mlrfit5 <- lm(Logarea ~ RH+temp+RH:temp+I(RH^2) + I(temp^2), data=subdata)

#help us to determine which model is best based on statistics. 
compareFitStats <- function(fit1, fit2, fit3, fit4, fit5){
	require(MuMIn)
	fitStats <- data.frame(fitStat = c("Adj R Square", "AIC", "AICc", "BIC"),
	    col1 = round(c(summary(fit1)$adj.r.squared, AIC(fit1), 
									MuMIn::AICc(fit1), BIC(fit1)), 3),
			col2 = round(c(summary(fit2)$adj.r.squared, AIC(fit2), 
									MuMIn::AICc(fit2), BIC(fit2)), 3), 
	    col3 = round(c(summary(fit3)$adj.r.squared, AIC(fit3), 
	                MuMIn::AICc(fit3), BIC(fit3)), 3),
	    col4 = round(c(summary(fit4)$adj.r.squared, AIC(fit4), 
	                MuMIn::AICc(fit4), BIC(fit4)), 3),
	    col5 = round(c(summary(fit5)$adj.r.squared, AIC(fit5), 
	                MuMIn::AICc(fit5), BIC(fit5)), 3))
	#put names on returned df
	calls <- as.list(match.call())
	calls[[1]] <- NULL
	names(fitStats)[2:6] <- unlist(calls)
	fitStats
}

#higher adj R square is better fit; Lower AIC, AICc, and BIC is better. 
compareFitStats(mlrfit1, mlrfit2, mlrfit3, mlrfit4, mlrfit5)
```

#Plots

For these plots, we are visualizing the effect of the explanatory variables on the response variable which is our LogArea. From the 3D plot with the RH and temp as explanatory variables, we can see a random scatter of variables along with a plane, to help visualize the relationship between the mixed model. Based on the adjusted R square, we should assume a very small positive relationship between all of the variables.  

Our ggplot presents us with a correlation between the RH variable and log of the area. We can visualize somewhat of a negative relationship with only the RH as the explanatory variable. 
```{r, warning=FALSE, message=FALSE}

p <- ggplot(subdata, aes(x=RH, y=Logarea)) + geom_point() + geom_smooth(method = "lm", aes(col=Logarea))
p

grid.lines=40
x.pred <- seq(min(subdata$RH), max(subdata$RH), length.out = grid.lines)
y.pred <- seq(min(subdata$temp), max(subdata$temp), length.out = grid.lines)
xy <- expand.grid(RH=x.pred, temp=y.pred)
z.pred <- matrix(predict(mlrfit5, newdata = xy, nrow=grid.lines, ncol=grid.lines))

plot3d(x=subdata$RH, y=subdata$temp, z=subdata$Logarea, cex=0.8, theta=20, phi=20, ticktype="detailed", xlab = "Relative Humidity in %", ylab = "Temperature in Celsius", zlab = "Log of Area")
surface3d(x=x.pred, y=y.pred, z=z.pred, color="Green")

yanModel <- formula(Logarea ~ RH+temp+RH:temp, data=subdata)
yanModel
```
